---
title: "R Markdown and Leaflet"
author: "Vandita Singh"
date: "2026-09-20"
output: html_document
---

---
title: "Exploring Manipal"
author: "Vandita Singh"
output:
  html_document:
    self_contained: true
---

# My Interactive Map

**Date Created:** `r format(Sys.Date(), "%B %d, %Y")`

This webpage presents an interactive map created using the **Leaflet** package in R. The map highlights Manipal and a few interesting locations around the campus area.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(leaflet)
```

## Interactive Map of Manipal

```{r map}
leaflet() %>%
  addTiles() %>%
  setView(
    lng = 74.7850,
    lat = 13.3500,
    zoom = 14
  ) %>%
  addMarkers(
    lng = 74.7850,
    lat = 13.3500,
    popup = "<b>Manipal</b><br>My university town"
  ) %>%
  addCircleMarkers(
    lng = 74.7925,
    lat = 13.3520,
    radius = 8,
    popup = "<b>MIT Manipal</b><br>Manipal Institute of Technology",
    label = "MIT Manipal"
  ) %>%
  addCircleMarkers(
    lng = 74.7890,
    lat = 13.3505,
    radius = 8,
    popup = "<b>Manipal Lake</b><br>A popular location in Manipal",
    label = "Manipal Lake"
  ) %>%
  addCircleMarkers(
    lng = 74.7840,
    lat = 13.3540,
    radius = 8,
    popup = "<b>End Point</b><br>A scenic location in Manipal",
    label = "End Point"
  ) %>%
  addControl(
    html = "<h4 style='margin:5px;'>My Manipal Map</h4>",
    position = "topright"
  )
```

## About the Map

The map above is interactive. You can:

- Zoom in and out using the **+** and **−** buttons.
- Move around the map.
- Click on the markers to see information about each location.
- Hover over markers to see their labels.

The map was created using the **Leaflet** package in R.

## Conclusion

This webpage demonstrates how R Markdown can be used to combine written content with an interactive geographic visualization. Leaflet makes it possible to create an interactive map directly within an HTML webpage.
